Title

### 2013-03-19 inc/hardware/introduction.tex
added new UEM design considerations chapter

>>>>

To satisfy the first restriction, many of the common elements of an electron microscope column must be redesigned to accomodate the larger beam area.
I will then describe how we have addressed the necessity of the large-area source in building the prototype UEM system begin constructed at UIC.
In order to allow flexibility or to meet some technical challenges presented by the above considerations, much of the system is custom built.
